Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets

### 2012-12-07 paper/paper.tex
paper

\section{Experimental Setup}
In order to determine which combination of preprocessing steps would results in the highest performance, we built a custom evaluation platform that iterates through all possible valid combinations of pipes and evaluates their performance. This led to nearly one hundred combinations, as each of the six tokenizer variations was run with and without bigramming, with and without stemming, etc. For consistency, the disjoint training and test sets used to evaluate each combination were identical for each iteration. To best observe the effects of training set size, training sizes of 50 to 1500 were tested in increments of 50, where each set is a superset of the previous set with 50 new randomly chosen instances, as opposed to using n-fold cross validation, which would not display this characteristic evenly across varied training and testing sizes. To evaluate this large set of results, we have chosen three relevant evaluation metrics. The first is precision, or the ratio of correctly labeled tweet instances to the number of instances assigned a particular label (`apple' or `none' in our case). Higher values for this metric mean fewer false positives for the desired company, which is the overall goal in this classification task. The second metric was recall, or the ratio of correctly classified instances out of the full set of instances which should have the label in question. This metric is less relevant to our purpose, but still interesting. The sheer scale of Twitter means missing even half of the tweets mentioning a company and mislabeling them as about `none' is of little consequence. Finally we use the F1 metric, a standard combination of precision and recall that is useful in determining overall if some pipeline combination is better than another in both precision and recall.

@@

\section{Conclusion and Future Work}

@@

Yerva et al demonstrate a system of using background knowledge and relatedness, in which current information in the Twitter stream is used to more accurately estimate the priors for a Naive Bayes classification (\citeauthor{journals/ijcsa/YervaMA12}).\\

@@

Sriram et al found that utilizing author profiles provide a good method for further disambiguation of tweets into categories, as authors tend to tweet messages within a limited set of categories. They also delineate a set of eight features (8F) used for training, instead of using the Bag-of-Words approach as we do. Through further analysis of the most useful features found in our approach, we could also choose a discrete set of binary or n-ary features most relevant to this classification task and explore its accuracy versus BOWc (\citeauthor{Sriram:2010:STC:1835449.1835643}).

\section{Contributions}
We have built several reusable Java components that extend the Mallet API for processing of data from Twitter. We created a TweetJsonIterator that accepts a file of Twitter's JSON-formatted tweets and creates training Instances containing their values for easy processing during model training. We have implemented several Pipes that can be reused or easily modified to suit a similar Twitter processing purpose. These include Link2Title, Stemmer, SpellCheck, and Tokenize, the latter of which serves as a more extensible tokenizer than Mallet's default. All code is available through our project website. We also provide a corpus of 100,000 tweets selected by Apple-related keyword and our labeled data set of 2000 tweets. The bash scripts used to filter the data for near-duplicates and spam are also available for download.\\

>>>>

\section{Experimental Setup}
In order to determine which combination of preprocessing steps would result in the highest performance, we built a custom evaluation utility that iterates through all possible valid combinations of pipes and evaluates their performance. This led to nearly one hundred combinations, as each of six tokenizer variations was run with and without bigramming, with and without stemming, etc. For consistency, the disjoint training and test sets used to evaluate each combination were identical for each iteration. To best observe the effects of training set size, training sizes of 50 to 1500 were tested in increments of 50, where each set is a superset of the previous set with 50 new randomly chosen instances, as opposed to using n-fold cross validation, which would not display this characteristic evenly across varied training and testing sizes. To evaluate this large set of results, we have chosen three relevant evaluation metrics. The first is precision, or the ratio of correctly labeled tweet instances to the number of instances assigned a particular label (`apple' or `none' in our case). Higher values for this metric mean fewer false positives for the desired company, which is the overall goal in this classification task. The second metric was recall, or the ratio of correctly classified instances out of the full set of instances which should have the label in question. This metric is less relevant to our purpose, but still interesting. The sheer scale of Twitter means missing even half of the tweets mentioning a company and mislabeling them as about `none' is of little consequence. Finally we use the F1 metric, a standard combination of precision and recall that is useful in determining overall if some pipeline combination is better than another in both precision and recall.

@@

\section{Contributions and Future Work}
We have presented a pipeline for processing tweets that increases accuracy and precision of the resulting models. We introduce a layered approach to tokenization that sees improvements over other rule-based methods. We have built several reusable Java components that extend the Mallet API for processing of data from Twitter. We created a TweetJsonIterator that accepts a file of Twitter's JSON-formatted tweets and creates training Instances containing their values for easy processing during model training. We have implemented several Pipes that can be reused or easily modified to suit a similar Twitter processing purpose. These include Link2Title, Stemmer, SpellCheck, and Tokenize, the latter of which serves as a more extensible tokenizer than Mallet's default. We release our testing utility as a new way of comparing multiple similar pipelines. All code is available through our project website. We also provide a corpus of 100,000 tweets selected by Apple-related keyword and our labeled data set of 2000 tweets. The bash scripts used to filter the data for near-duplicates and spam are also available for download.\\

@@

Yerva et al demonstrate a system of using background knowledge and relatedness, in which current information in the Twitter stream is used to more accurately estimate the priors for a Naive Bayes classification (\citeauthor{journals/ijcsa/YervaMA12}). We believe that inclusion of this in our method could allow us to perform more accurate disambiguation.\\

@@

Sriram et al found that utilizing author profiles provide a good method for further disambiguation of tweets into categories, as authors tend to tweet messages within a limited set of categories. They also delineate a set of eight features (8F) used for training, instead of using the Bag-of-Words approach as we do. Through further analysis of the most useful features found in our approach, we could also choose a discrete set of binary or n-ary features most relevant to this classification task and explore its accuracy versus Bag-of-Words (\citeauthor{Sriram:2010:STC:1835449.1835643}).
